% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Prasang Sharma}
\newcommand{\CVTitle}{Prasang Sharma's CV}
\newcommand{\CVNote}{CV compiled on {\today} for MITACS}
\newcommand{\CVWebpage}{https://prasang7.github.io/}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}

\href{http://vit.ac.in/}
{VIT University, Chennai, India}

\par
\href{\CVWebpage}{Website}
\,\SubBulletSymbol
\,\href{https://github.com/prasang7}{Github}
\,\SubBulletSymbol
\,\href{https://in.linkedin.com/in/prasang7}{Linkedin}
\,\SubBulletSymbol
\,\href{https://www.behance.net/prasang7}{Design Portfolio}

\par
\href{mailto:prasang.sharma7@gmail.com}
{prasang.sharma7@gmail.com}
\,\SubBulletSymbol\,
+91\,86810-70970

\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{http://vit.ac.in/}
{\textbf{Vellore Institute of Technology}},
Chennai, Tamil Nadu, India
\hfill
{Expected May 2018}

\GapNoBreak
\BulletItem
Bachelor of Technology (B.Tech.) in Computer Science
\begin{detail}
\SubBulletItem
Cumulative GPA (after 4 semester): 9.01/10.00
\SubBulletItem
Relevant Coursework: OOPS, Data Structures, Algorithm Analysis, DBMS.
\end{detail}


%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%

\section
{Work Experience}
{Work Experience}
{PDF:Work Experience}

\href{https://www.engineerbabu.com/}
{\textbf{EngineerBabu Inc}},
Indore, Madhya Pradesh, India
\hfill
{Dec 2015 - Jan 2016}
\GapNoBreak
\BulletItem
Software Development Intern
\begin{detail}
\SubBulletItem
Worked on MotorBabu App - vehicle repair \& service booking app. 
\SubBulletItem
Collaboratively worked with senior Android Developers. 
\SubBulletItem
Created the currently used login/signup system, and many internal pages/activites of the app.
\SubBulletItem
Learned about various API calls and methods in Android, to fetch/send data to remote servers.
\end{detail}

\Gap
\href{}
{\textbf{VOLOC}}, VIT Chennai
\hfill
{April 2016 - Present}
\GapNoBreak
\BulletItem
Lead Android Developer \& Intern
\begin{detail}
\SubBulletItem
Online learning portal providing e-learning with - Videos, Quizzes, and Documentation.
\SubBulletItem
Lead a team of 8 Android Developers to collaboratively build VOLOC's Android client on Github.
\SubBulletItem
Created base activities/pages of app along with UI/UX and base functionalities.
\end{detail}


%%%%%%%%%%%%%%%%%%%%%
%%     PROJECTS    %%
%%%%%%%%%%%%%%%%%%%%%

\section
{Projects}
{Projects}
{PDF:Projects}

\Gap
\href{https://play.google.com/store/apps/details?id=com.dert}
{\textbf{DERT}}, Doctor's Emergency Rescue Task App
\hfill
{}
\GapNoBreak
\BulletItem
Co-founder and Android Developer
\begin{detail}
\SubBulletItem
Project Description: Cross-platform mobile application - Solves social issue by providing safety to doctors.
\SubBulletItem
Created DERT's android client, along with designing UI/UX of both iOS and Android app.
\SubBulletItem
Accepted by Indian Medical Association and used by 140+ doctors in Dehradun.
\SubBulletItem
Tech: Multi-Threading, Runtime Permissions, API calls (Volley), Google Cloud Messaging - Push Notifications.   
\end{detail}

\Gap 
\href{https://play.google.com/store/apps/details?id=com.cambuzz.internetcabin.cambuzzvitcc}
{\textbf{Cambuzz}}, Open Source Networking Platform
\hfill
{}
\GapNoBreak
\BulletItem
Lead App Developer, Team of 9 students (Webapp \& Android)
\begin{detail}
\SubBulletItem
Project Description: Centralized information system, with track teacher feature and in campus Q/A forum.
\SubBulletItem
Created cambuzz-live-feed to bring all the news about our campus on cambuzz android client.
\SubBulletItem
Successfully used by 1600+ students.
\SubBulletItem
Tech: API calls (Volley), SQLite services, Push Notification system, Material Design.
\end{detail}

\Gap
\href{https://play.google.com/store/apps/details?id=com.iotaconcepts.aurum&hl=en}
{\textbf{Aurum}}, Healthcare Application - targeting rural India
\hfill
{}
\GapNoBreak
\BulletItem
Android Dev and Design Lead
\begin{detail}
\SubBulletItem
Project Description: Healthcare assistance app: tracks diseases, and displays nearby health centers. 
\SubBulletItem
Created login/signup system, along with the UI/UX of the app, and integrated Maps API.
\SubBulletItem
This app led us to the National Finals of IBM-RTBI Hackathon, IIT Madras.
\SubBulletItem
Tech: AsyncTasks, Google Maps API, Custom disease mapping algorithm, Material Design.
\end{detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTIVITIES AND AWARDS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Awards and\hfill \break Activities}
{Activities and Awards}
{PDF:Activities and Awards}

\BulletItem
World Finalist (Top 10), World UX Championship (World Usability Congress 2016) 
\BulletItem
Winner, Make-a-thon (App Development Hackathon), VIT Chennai, 2015.
\BulletItem
Winner, DESIGNation'15 (Graphic Design Competition), VIT Chennai, 2015.
\BulletItem
Active Member - Android Club, VIT Chennai. Organiser of app based treasure hunt event.
\BulletItem
Academic Excellence Award, VIT Chennai, 2015.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SKILLS AND INTERESTS  %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Skills and\hfill \break Interests}
{Skills and Interests}
{PDF:Skills and Interests}

\BulletItem
Language: English (Fluent), Hindi (Native) and Spanish (Elementary Proficiency) 
\BulletItem
Technical: Android Application Development, Java, C\#, WebDev Languages (HTML, CSS), {\LaTeX}.
\BulletItem
Dev Ops: Linux, Git, Android Studio, Adobe Photoshop.   
\BulletItem
Interest: Application Development, Product Design, Machine Learning.

\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\begin{flushright}
\UseNoteFont%
%%[\textit{\CVNote}]%
%%\hspace{2.0mm}\null
\end{flushright}

\label{LastPage}~
\end{document}
